Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks

### 2016-10-15 paper.tex
Remove some comments and add notes
Little changes

\subsection{Recurrent Neural Network}
\label{sec:architecture}
Next, we design a network that takes a sequence of 3D-CNN-f6 features from a video, and returns a sequence of class probabilities for each element in the sequence. We use LSTM layers, followed with dropout with $p = .5$ and a fully connected layer with a softmax activation. Figure~\ref{fig:global_pipeline} shows the proposed architecture. Different configurations of the number of LSTM layers and the number of cells have been tested and will be reviewed in the following sections.

@@

where $q$ is the predicted probability distribution and $p$ the ground truth probability distribution. In our experiments, we set $\rho$ = .3.

The network was trained with a 256 batch size and 20 \textit{timesteps} as input sequence.
The optimezer function used was the RMSprop~\cite{dauphin2015rmsprop} with a learning rate set to $10^{-5}$. In total the network was trained with 100 epochs.

@@

% \begin{table}[h]
% \begin{center}
% \begin{tabular}{|l|c|c|}
% \hline
% \textbf{Architecture} & \textbf{mAP} & \textbf{Hit@3} \\
% \hline\hline
% 3 x 1024-LSTM & 0.5635 & 0.7437 \\
% 2 x 512-LSTM & 0.5492 & 0.7364 \\
% 1 x 512-LSTM & \bf0.5938 & \bf0.7576 \\
% \hline
% \end{tabular}
% \end{center}
% \caption{Results for classification task comparing different deep architectures. All values with
%          only video features on the validation dataset.}
% \label{table:classification_by_architecture}
% \end{table}
%
% \begin{table}[h]
% \begin{center}
% \begin{tabular}{|l|c|c|c|}
% \hline
% \textbf{$\gamma$} & \textbf{$k=0$} & \textbf{$k=5$} & \textbf{$k=10$} \\
% \hline
% \textbf{0.2} & 0.20732 & \bf0.22513 & 0.22136 \\
% \textbf{0.3} & 0.19854 & 0.22077 & 0.22100 \\
% \textbf{0.5} & 0.19035 & 0.21937 & 0.21302 \\
% \hline
% \end{tabular}
% \end{center}
% \caption{mAP with an IOU threshold of $0.5$ over validation dataset. Here there is a comparison
% between values of $k$ and $\gamma$ on post processing.}
% \label{table:detection_postprocessing_comparison}
% \end{table}
% \end{multicols}

% \begin{figure}
% \centering
% \subfloat[][]{
% \begin{table}[h]
% \begin{center}
% \begin{tabular}{|l|c|c|}
% \hline
% \textbf{Architecture} & \textbf{mAP} & \textbf{Hit@3} \\
% \hline\hline
% 3 x 1024-LSTM & 0.5635 & 0.7437 \\
% 2 x 512-LSTM & 0.5492 & 0.7364 \\
% 1 x 512-LSTM & \bf0.5938 & \bf0.7576 \\
% \hline
% \end{tabular}
% \end{center}
% \caption{Results for classification task comparing different deep architectures. All values with
%          only video features on the validation dataset.}
% \label{table:classification_by_architecture}
% \end{table}
% }
% \qquad
% \begin{table}[h]
% \begin{center}
% \begin{tabular}{|l|c|c|c|}
% \hline
% \textbf{$\gamma$} & \textbf{$k=0$} & \textbf{$k=5$} & \textbf{$k=10$} \\
% \hline
% \textbf{0.2} & 0.20732 & \bf0.22513 & 0.22136 \\
% \textbf{0.3} & 0.19854 & 0.22077 & 0.22100 \\
% \textbf{0.5} & 0.19035 & 0.21937 & 0.21302 \\
% \hline
% \end{tabular}
% \end{center}
% \caption{mAP with an IOU threshold of $0.5$ over validation dataset. Here there is a comparison
% between values of $k$ and $\gamma$ on post processing.}
% \label{table:detection_postprocessing_comparison}
% \end{table}
%
% \end{figure}

@@

>>>>

\subsection{Recurrent Neural Network}
\label{sec:architecture}
Next, we design a network that takes a sequence of 3D-CNN-f6 features from a video, and returns a sequence of class probabilities for each element in the sequence. We use LSTM layers, followed with dropout with $p = 0.5$ and a fully connected layer with a softmax activation. Figure~\ref{fig:global_pipeline} shows the proposed architecture. Different configurations of the number of LSTM layers and the number of cells have been tested and will be reviewed in the following sections.

@@

where $q$ is the predicted probability distribution and $p$ the ground truth probability distribution. In our experiments, we set $\rho = 0.3$.

The network was trained with batches of 256 samples, back-propagating the error during 20 time-steps per sample.
The optimizer function used was the RMSprop~\cite{dauphin2015rmsprop} with a learning rate set to $10^{-5}$. In total the network was trained with 100 epochs.

@@

@@

% ALBERTO: que més explico a les conclusions
